An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks

### 2017-12-17 Report/paper.tex

\subsection{Oversegmentation correction}
In this section we provide a method to fix the oversegmentation of the word image caused by the previous steps.
To achieve this we process the potential segmentation points with a few rule based filters, to remove redundant and incorrect segmentation points.
The final decision to which segmentation points we retain is made by a neural network.

@@

Character segmentation is another ..
The proposed oversegmentation serves the intended purpose, however more rule-based postprocessing steps are needed to reduce the amount of incorrect segmentation points the neural network has to process. Combinations with other approaches could also yield better results

>>>>

\subsection{Oversegmentation correction}
In this section we provide techniques to verify the correctness of these segmentation points. 
\citep{evalsplitpoints} discusses three approaches to evaluate segmentation point correctness: rule based techniques, cost function optimization based methods and machine learning based procedures. [6:39]
In this paper we discuss machine learning based approaches precedented by a few rule based techniques.

@@

Character segmentation is another ..
The proposed oversegmentation serves the intended purpose, however more rule-based postprocessing steps are needed to reduce the amount of incorrect segmentation points the neural network has to process.
Combinations with other approaches are also more likely provide better results.

The neural network ..
